Taking Dyads Seriously:\\A Latent Network Approach to Dyadic Analysis

### 2017-10-28 paper/netsMatter.tex
v2
600 grit sand paper
not sure if title is right.

% add watermark
\usepackage{draftwatermark}
\SetWatermarkText{Version 1.0}
\SetWatermarkScale{.5}
\SetWatermarkColor[gray]{0.9}

@@

% \title{Taking Dependencies Seriously:\\A Latent Network Approach to Dyadic Analysis}
\title{Taking Conditional Independence Seriously:\\A Latent Network Approach to Dyadic Analysis}
\vspace{\baselineskip}

@@

	Much of international relations scholarship concerns dyads: dyadic hypotheses and propositions, and especially dyadic data. Yet, contemporary research brushes aside the complications that come with analyzing relational data that are interdependent. Dyadic observations do not typically satisfy the conditional independence criterion required for many statistical approaches. As a result, many studies often produce results with biased coefficient estimates and poorly calibrated standard errors. These biases have profound consequences for evaluating parametric models. We present an alternative, regression-based approach that accounts for the dependencies that complicate inferential analysis in the context of relational data. To highlight the utility of this framework for studying relational data, we first present a simulation exercise highlighting the model's ability to account for the dependencies that emerge in relational data. In addition, we replicate five prominent studies in recent international relations scholarship, comparing the standard approach to our alternative. For each study, we find that conventional methods overstate the effect of key variables in the study of interstate conflict (and trade), underestimate the uncertainty in these effects, and in some cases lead researchers to faulty conclusions about the statistical significance and substantive importance of their variables. Further, we show that our approach dominates in terms of out-of-sample cross-validations, rendering it more useful in forecasting applications and in modeling the data generating process behind outcomes of interest.
\end{abstract}
}}

@@

\newpage
% Bib stuff
\clearpage
\bibliography{/Users/s7m/whistle/master}
% \bibliography{/Users/mdw/Git/whistle/master}
%\bibliography{/Users/cassydorff/ProjectsGit/master}
% \bibliographystyle{authordate1}
\bibliographystyle{sm}
% \clearpage
% \section*{All About Us}

>>>>

% % add watermark
% \usepackage{draftwatermark}
% \SetWatermarkText{Version 1.0}
% \SetWatermarkScale{.5}
% \SetWatermarkColor[gray]{0.9}

@@

% \title{Taking Dependencies Seriously:\\A Latent Network Approach to Dyadic Analysis}
\title{Taking Dyads Seriously:\\A Latent Network Approach to Dyadic Analysis}
\vspace{\baselineskip}

@@

	Much international relations scholarship concerns dyads: dyadic hypotheses and especially dyadic data. Yet, contemporary research brushes aside the complications that come with analyzing relational data that are interdependent. Dyadic observations do not typically satisfy the conditional independence criterion required for many statistical approaches. As a result, many studies often produce results with biased coefficient estimates and poorly calibrated standard errors. These biases have profound consequences for evaluating parametric models. We present an alternative, regression-based approach that accounts for the dependencies that complicate inferential analysis in the context of relational data. To highlight the utility of this framework for studying relational data, we first present a simulation exercise highlighting the model's ability to account for the dependencies that emerge in relational data. In addition, we replicate five prominent studies in recent international relations scholarship, comparing the standard approach to our alternative. For each study, we find that conventional methods overstate the effect of key variables in the study of interstate conflict (and trade), underestimate the uncertainty in these effects, and in some cases lead researchers to faulty conclusions about the statistical significance and substantive importance of their variables. Further, we show that our approach dominates in terms of out-of-sample cross-validations, rendering it more useful in forecasting applications and in modeling the data generating process behind outcomes of interest.
\end{abstract}
}}

@@

\newpage
% Bib stuff
\clearpage
%\bibliography{/Users/s7m/whistle/master}
\bibliography{/Users/mdw/Git/whistle/master}
%\bibliography{/Users/cassydorff/ProjectsGit/master}
% \bibliographystyle{authordate1}
\bibliographystyle{sm}
% \clearpage
% \section*{All About Us}
